<!-- R Commander Markdown Template -->

Replace with Main Title
=======================

### AJITH N

### `r as.character(Sys.Date())`

```{r echo=FALSE}
# include this code chunk as-is to set options
knitr::opts_chunk$set(comment=NA, prompt=TRUE, out.width=750, fig.height=8, fig.width=8)
library(Rcmdr)
library(car)
library(RcmdrMisc)
```

```{r}
Dataset <- readXL("D:/BA FILES/STATISTICS 2/Data Set-20240206/BComCA.xlsx", rownames=FALSE, header=TRUE, na="", 
  sheet="B.COM CA", stringsAsFactors=TRUE)
```

```{r}
library(abind, pos=16)
```


```{r}
library(e1071, pos=17)
```



1. What is the average % of the scores (12th %) of those who opted for Commerce UG
Degree in the year 2021?
```{r}
numSummary(Dataset[,"PercentageMarks", drop=FALSE], statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,
  .25,.5,.75,1))
```
 interpretation

 1.the average score of the student those who joined in commerce degree is 65%
 
 2. 50% of students scored more than 50% and remaining 50% of them scored below 50%
 
 3. top 25% of students score 73%
 

### Histogram: PercentageMarks
```{r}
with(Dataset, Hist(PercentageMarks, scale="frequency", breaks="Sturges", col="darkgray"))
```
 interpretation
 
 1.more number of students got 50 to 75% of marks and less number of students got 85 to 95%


### Boxplot: ~ PercentageMarks
```{r}
Boxplot( ~ PercentageMarks, data=Dataset, id=list(method="y"))
```


### Histogram: X12th.Marks
```{r}
with(Dataset, Hist(X12th.Marks, groups=Gender, scale="frequency", breaks="Sturges", col="darkgray"))
```
 interpretation
 
 1. the more number of girl students got 400 to 450 marks and less number of them got 550 to 600

 2. number of lowet mark his very low of them got

3. the more number of girl students got 400 to 450 marks and less number of them got 550 to 600

4. comparing to boys and girls boys are scored high scores


```{r}
Dataset <- readXL("D:/BA FILES/STATISTICS 2/Data Set-20240206/BSc IT.xlsx", rownames=FALSE, header=TRUE, na="", 
  sheet="B.SC IT", stringsAsFactors=TRUE)
```


### Numerical Summaries: Dataset
2. What is the average % of the scores (12th %) of those who opted for Computer
Science UG Degree in the year 2021?
```{r}
numSummary(Dataset[,"PercentageMarks", drop=FALSE], statistics=c("mean", "sd", "IQR", "quantiles"), quantiles=c(0,
  .25,.5,.75,1))
```

interpretation

1.the average score of the student those who joined in computer science degree is 64%

2. 50% of students scored more than 50% and remaining 50% of them scored below 50%

 3. top 25% of students score 73%



### Histogram: PercentageMarks
```{r}
with(Dataset, Hist(PercentageMarks, scale="frequency", breaks="Sturges", col="darkgray"))
```



### Boxplot: ~ PercentageMarks
```{r}
Boxplot( ~ PercentageMarks, data=Dataset, id=list(method="y"))
```

```{r}
Dataset <- readXL("D:/BA FILES/STATISTICS 2/Data Set-20240206/CombinedITCA.xlsx", rownames=FALSE, header=TRUE, 
  na="", sheet="MergedDataset", stringsAsFactors=TRUE)
```




### Independent-Samples t-Test: PercentageMarks ~ PgmName
```{r}
t.test(PercentageMarks ~ PgmName, alternative = "two.sided", conf.level = .95, var.equal = FALSE, data = Dataset)
```


### Independent-Samples t-Test: PercentageMarks ~ Gender
```{r}
t.test(PercentageMarks ~ Gender, alternative = "two.sided", conf.level = .95, var.equal = FALSE, data = Dataset)
```


### Histogram: PercentageMarks
```{r}
with(Dataset, Hist(PercentageMarks, groups=PgmName, scale="frequency", breaks="Sturges", col="darkgray"))
```


### Histogram: PercentageMarks
```{r}
with(Dataset, Hist(PercentageMarks, groups=Gender, scale="frequency", breaks="Sturges", col="darkgray"))
```


### Independent-Samples t-Test: X12th.Marks ~ Gender
```{r}
t.test(X12th.Marks ~ Gender, alternative = "two.sided", conf.level = .95, var.equal = FALSE, data = Dataset)
```


### Histogram: X12th.Marks
```{r}
with(Dataset, Hist(X12th.Marks, groups=Gender, scale="frequency", breaks="Sturges", col="darkgray"))
```

